import data:
```{r}
library(stars)
r = read_stars("NDVI2019_ClassificationImg_10m.tif") |> setNames("NDVI")
r
p = st_read("PixelCoordinates_Polygon.geojson")
```

transform polygon to UTM 22 S:
```{r}
p.utm = st_transform(p, st_crs(r))
```

compute the variance of the raster image:
```{r}
(v = var(as.vector(r[[1]])))
```

The different grid sizes:
```{r}
gridsizes = c(10, 20, 50, 100, 200, 500, 1000, 2000, 5000, 10000)
thinning = gridsizes / 10
```

Compute the standard errors associated with the different grid sizes, for
random sampling:
```{r}
(n = prod(dim(r)) / (thinning^2))
(se.random_sampling = sqrt(v/n))
names(se.random_sampling) = gridsizes
se.random_sampling
```

Now do this for regular sampling, using Ripley 1981:
```{r}
library(gstat)
set.seed(1353)
pts = st_sample(p.utm, 10000)
r.sample = st_extract(r, pts)
dist = c(10, 20, 50, 100, 200, 500, seq(1000, 10000, 500))
v = variogram(NDVI~1, r.sample, boundaries = dist)
plot(v)
m = "Exp"
v0 = vgm(.1, m, 100)
(v.model = fit.variogram(v, vgm(.1, m, 500, add.to = v0)))
plot(v, v.model)
```

Compute the mean point-point covariance function value, using random sampling
(MC integration):
```{r}
n = 1e4
make_unif_pts = function(bbox, n) {
	x = runif(n, bbox["xmin"], bbox["xmax"])
	y = runif(n, bbox["ymin"], bbox["ymax"])
	as.matrix(cbind(x = x, y = y))
}

mean_cov = function(x, y, model) {
	d = if (missing(y))
			as.vector(as.matrix(dist(x)))
		else {
			all = rbind(x, y)
			n1 = nrow(x)
			n2 = nrow(y)
			as.vector(as.matrix(dist(all))[(n1+1):(n1+n2),1:n1])
		}
	mean(variogramLine(v.model, covariance = TRUE, dist_vector = d, n)$gamma)
}

x = make_unif_pts(st_bbox(r), n)
y = make_unif_pts(st_bbox(r), n)
(C_mean = mean_cov(x, y, v.model))
```

Create a function that computes the SE using Ripley's 1981 eq. 3.4 (page 23),
and use it:
```{r}
make_grid = function(size, bbox, n = Inf) {
	x = seq(bbox["xmin"], bbox["xmax"], size)
	y = seq(bbox["ymin"], bbox["ymax"], size)
	grd = as.matrix(expand.grid(x = x, y = y))
	if (n < nrow(grd))
		grd = grd[sample(nrow(grd), n), ]
	grd
}

compute_se = function(size, model, maxpts = 1e4, C_mean) {
	grd = make_grid(size, st_bbox(r), maxpts)
	pts = make_unif_pts(st_bbox(r), maxpts)
	# eq 3.4, RHS part:
	var = mean_cov(grd, model = v.model) -
		2 * mean_cov(grd, pts, v.model) + C_mean
	sqrt(var)
}

#sel = -(1:5)
sel = TRUE
se = sapply(gridsizes[sel], compute_se, model = v.model, C_mean = C_mean)
names(se) = gridsizes[sel]
se
se.random_sampling 
```

Save:
```{r}
rm(r) # big
save.image("sampling.rda")
```
